### 2022-03-11 unif/unif.tex
intro

% In Sect.~\ref{sec:unif:indexing} we discuss a higher-order extension of fingerprint indexing,
% a technique to filter out terms that are not unifiable with a given
% query term from a set of terms. 
To more efficiently find terms (in a large term set) that are unifiable with a given query term,
we developed a higher-order extension of fingerprint indexing \cite{ss-12-fp-indexing}
(Sect.~\ref{sec:unif:indexing}).
We implemented our procedure, several oracles,
and the fingerprint index in
the Zipperposition prover (Sect.~\ref{sec:unif:implementation}). Since a
straightforward implementation of the JP procedure already existed in
Zipperposition, we used it as a baseline to evaluate the performance of our
procedure (Sect.~\ref{sec:unif:evaluation}). The results show substantial
performance improvements.

@@

\looseness=-1
Contrary to first-order unification, there is no widely available benchmark set 
designed solely for evaluating performance of higher-order
unification algorithms. Thus, we used all 2606 monomorphic higher-order theorems
from the TPTP library \cite{gs-17-tptp} and 832 monomorphic higher-order
Sledgehammer (SH) generated problems \cite{ns-13-leo2sh} as our benchmarks.\footnote{An archive with raw
results, all used problems, and scripts for running each configuration is
available at \url{http://doi.org/10.5281/zenodo.4269591}}
Many TPTP problems require synthesis of complicated unifiers,
whereas SH problems are only mildly higher-order---many of them are
solved with first-order unifiers.

\looseness=-1
We used the naive implementation of the JP procedure (\textbf{jp}) as a baseline
to evaluate the performance of our procedure. We compare it with the complete
variant of our procedure (\textbf{cv}) and pragmatic variants
(\textbf{pv}) with several different configurations of limits for
applied bindings. All other Zipperposition parameters have been fixed to the values of
a variant of a well-performing configuration we used for the CASC-27 theorem proving competition \cite{gs-19-casc27}.
The cv configuration and all of the pv
configurations use only pattern unification as an underlying oracle. To test
the effect of oracle choice, we evaluated the complete variant
in eight combinations: with no oracles
(\textbf{n}), with only fixpoint (\textbf{f}), pattern (\textbf{p}), or solid (\textbf{s}) oracle,
and with their combinations: \textbf{fp}, \textbf{fs}, \textbf{ps}, \textbf{fps}.

>>>>

% In Sect.~\ref{sec:unif:indexing} we discuss a higher-order extension of fingerprint indexing,
% a technique to filter out terms that are not unifiable with a given
% query term from a set of terms. 
To more efficiently find terms (in a large term set) that are unifiable with a given query term,
we developed a higher-order extension of fingerprint indexing \cite{ss-12-fp-indexing}
(Sect.~\ref{sec:unif:indexing}).
We implemented our procedure, several oracles,
and the fingerprint index (Sect.~\ref{sec:unif:implementation}) in
the Zipperposition prover \cite{sc-supind-17,sc-15-simon-phd}. Since a
straightforward implementation of the JP procedure already existed in
Zipperposition, we used it as a baseline to evaluate the performance of our
procedure (Sect.~\ref{sec:unif:evaluation}). The results show substantial
performance improvements.

@@

\looseness=-1
Contrary to first-order unification, there is no widely available benchmark set 
designed solely for evaluating performance of higher-order
unification algorithms. Thus, we used all 2606 monomorphic higher-order theorems
from the TPTP 7.2.0 library \cite{gs-17-tptp} and 832 monomorphic higher-order
Sledgehammer (SH) generated problems \cite{ns-13-leo2sh} as our benchmarks.\footnote{An archive with raw
results, all used problems, and scripts for running each configuration is
available at \url{http://doi.org/10.5281/zenodo.4269591}}
Many TPTP problems require synthesis of complicated unifiers,
whereas SH problems are only mildly higher-order---many of them are
solved with first-order unifiers.

\looseness=-1
We used the naive implementation of the JP procedure (\textbf{jp}) as a baseline
to evaluate the performance of our procedure. We compare it with the complete
variant of our procedure (\textbf{cv}) and pragmatic variants (\textbf{pv}) with
several different configurations of limits for applied bindings. All other
Zipperposition parameters have been fixed to the values of a variant of a
well-performing configuration we used for the 2019 installment of the higher-order
division of CASC theorem proving competition \cite{gs-19-casc27}. The cv
configuration and all of the pv configurations use only pattern unification as
an underlying oracle. To test the effect of oracle choice, we evaluated the
complete variant in eight combinations: with no oracles (\textbf{n}), with only
fixpoint (\textbf{f}), pattern (\textbf{p}), or solid (\textbf{s}) oracle, and
with their combinations: \textbf{fp}, \textbf{fs}, \textbf{ps}, \textbf{fps}.
